Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-23 analysis/paper/paper.Rmd
Add 5 year impact factor to journal table

```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(journal) %>%
  select(-percent) %>%
  rename(Journal = journal) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  autofit() %>%
  set_caption(
    "Journal titles selected for inclusion and the number (n) of articles from each journal that were evaluated."
  )
```

>>>>

```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
journal <-
  tabyl(rrpp, journal) %>%
  select(-percent)

distinct(rrpp, journal, IF_5year) %>%
  left_join(journal, by = "journal") %>% 
  rename(Journal = journal,
         `5 Year IF` = IF_5year) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  autofit() %>%
  set_caption(
    "Journal titles selected for inclusion, their respective five year impact factors as of 2022 and the number (n) of articles from each journal that were evaluated."
  )
```
